A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
A tense moment

Small scale experiments (not presented here) were performed to identify
suitable heuristics for selecting a label class and a vertex within a label
class selection. Our heuristic of choice selects the label class with the
smallest $\min(|\setG|,|\setH|)$. From this class, a vertex is selected from
$\setG$ with maximum degree if $\graphH$ is sparse and with minimum degree if
$\graphH$ is dense. We discuss this further in \cref{sec:comparison}.

@@

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times
against number of problem instances solved.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2,000 of the 4,110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, \McSplit\ was the fastest algorithm
on 87\% of the 3,506 instances that
could be solved by at least one of the four algorithm in less than than
1,000 seconds.

>>>>

Small scale experiments (not presented here) were performed to identify
suitable heuristics for selecting a label class and a vertex within a label
class selection. Our heuristic of choice selects the label class with the
smallest $\max(|\setG|,|\setH|)$. From this class, a vertex is selected from
$\setG$ with maximum degree if $\graphH$ is sparse and with minimum degree if
$\graphH$ is dense. We discuss this further in \cref{sec:comparison}.

@@

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times
against number of problem instances solved.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2,000 of the 4,110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, \McSplit\ is the fastest algorithm
on 87\% of the 3,506 instances that
could be solved by at least one of the four algorithm in less than than
1,000 seconds.
